\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}

\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}

\begin{document}

\begin{center}
    \textbf{\Huge kamran ali} \\
    \href{mailto:kamranchohan740@gmail.com}{kamranchohan740@gmail.com}
\end{center}

\vspace{1cm}

\section{Professional Summary}
Professional summary will be added here.  This section should be tailored to highlight relevant skills and experience for a full-stack MERN developer position at xyz.  Quantifiable achievements should be included.  For example: "Highly motivated and results-oriented full-stack developer with 2+ years of experience in designing, developing, and deploying robust web applications using the MERN stack. Proven ability to deliver high-quality projects on time and within budget. Expertise in [mention specific technologies]."


\section{Experience}
\subsection{Full Stack Developer}
\textbf{xyz} \\
\textit{MERN} \\

\begin{itemize}[noitemsep]
    \item  [Responsibility 1:]  Add a specific responsibility and quantifiable achievement. For example: "Developed and deployed three key features for a high-traffic web application, resulting in a 15% increase in user engagement."
    \item  [Responsibility 2:] Add a specific responsibility and quantifiable achievement.  For example: "Improved application performance by 20% through optimization of database queries and code refactoring."
    \item  [Responsibility 3:] Add a specific responsibility and quantifiable achievement. For example: "Successfully integrated a new payment gateway, resulting in a 10% increase in sales conversions."
\end{itemize}


\section{Education}
% Add your education details here.  Example:
%\subsection{Master of Science in Computer Science}
%\textit{University Name}

\section{Skills}
% Add your skills here, focusing on MERN stack technologies. Examples:
% \begin{itemize}[noitemsep]
%     \item MongoDB
%     \item Express.js
%     \item React.js
%     \item Node.js
%     \item JavaScript
%     \item HTML5
%     \item CSS3
%     \item Git
%     \item Agile Development
% \end{itemize}

\end{document}