\documentclass{resume}

\usepackage[utf8]{inputenc}
\usepackage{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}

\begin{document}

\name{Kamran Ali}
\contact{kamranchohan740@gmail.com}

\title{Resume}

\begin{resume}

\section{Summary}
Professional summary detailing your career objectives and highlights of your experience. Adapt this section to showcase your strengths and skills.

\section{Education}
\begin{itemize}
\item[\textbullet] \textbf{Degree Title,} University Name, City, Country \\
Graduation Date \\
Brief description of your degree, GPA (if noteworthy), relevant courses, and achievements.
\end{itemize}

\section{Experience}
\begin{itemize}
\item[\textbullet] \textbf{Job Title,} Company Name, Employment Dates \\
A brief overview of your role, technical skills used, and achievements.
\end{itemize}

\section{Technical Skills}
\begin{itemize}
\item[\textbullet] \textbf{Programming Languages:} Proficient in JavaScript, with experience in developing web applications.
\item[\textbullet] \textbf{Machine Learning:} Certified in Machine Learning, proficient in NLP techniques, and familiar with ML algorithms and libraries.
\item[\textbullet] \textbf{Databases:} Experienced in MySQL, PostgreSQL, and MongoDB, including database design and management.
\item[\textbullet] \textbf{API Development:} Skilled in designing and developing APIs, ensuring secure and efficient data exchange.
\end{itemize}

\section{Certifications}
\begin{itemize}
\item[\textbullet] Machine Learning Engineer Certification \\
Issuing Authority, Year
\end{itemize}

\end{resume}

\end{document}